---
title: "USA Gun report 2010"
author: "Kaycee"
date: "21 June 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is a report on the number of murders in usa in 2010 by guns. data obtained at:


I will use this library in analysis of my data:

```{r loading-libs, message=FALSE}
library(tidyverse)
```

## and load the data I've already wrangled


```{r}
load("rda/murders.rda")
```

This is a scatterplot of the US gun murder rate and the code used to generate it
```{r murder-rate-by-state-and-region}
library(ggthemes)
library(ggrepel)
r<-murders %>% 
  summarise(rate=sum(total)/sum(population)*10^6) %>% .$rate
murders %>% ggplot(aes(population/10^6,total,label=abb))+
  geom_point(aes(col=region),size=3)+
  geom_abline(intercept = log10(r),lty=1,col="brown")+
  geom_text_repel()+
  scale_x_log10()+
  scale_y_log10()+
  ggtitle("USA Murder rate in 2010")+
  xlab("Population in millions(log scale)")+
  ylab("Total number of mrders(log scale)")+
  scale_color_discrete(name="Region")+
  theme_economist()














